---
title: "Stock_Exercise"
author: "Leo"
date: "2023-06-10"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Teste com rmarkdown

Just an exercise to practice rmarkdown 

For that we'll use a data set with the historic price of the stock SWK.

Gere we can see the first 30 register of the stock.

```{r , warning=FALSE}
library(quantmod)
library(dplyr)
stock_symbol <- "SWK"
start_date <- as.Date("2015-01-01")
end_date <- Sys.Date()
getSymbols(stock_symbol,from=start_date, to=end_date)
df_stock <- data.frame(SWK)
# summary(SWK)
head(df_stock, 30)
df_stock$Date <- index(SWK)

```

## Including Plots

With the data it's possible to make the the historic chart of the price.

```{r pressure, echo=FALSE, warning=FALSE}

# dia <- df_stock[,1]
dia <- df_stock$Date
# price <- select(df_stock, SWK.Close)
price <- df_stock$SWK.Close
print(colnames(df_stock))
plot(dia, price,type = "l")


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
